\textit{Urban and building multiscale co-simulation: case study implementations on two university campuses}

### 2016-04-18 latex/UMEM_CoSim.tex
updated clustering graphic

\subsection{Coupling process}
The coupling process of a simplified single zone model and contextual surrounding buildings is outlined in a previous study \citep{thomas2014multiscale}. This study forms the basis for the methodology in the current effort. This process utilizes the Design Performance Viewer (DPV) and associated work flow. The DPV is a tool written to extract and simulate an EnergyPlus input data file (IDF) from an Autodesk\textsuperscript{TM} Revit\textsuperscript{TM} BIM \citep{Schlueter2009}. The main philosophy behind the tool is rapid simulation of the building information model from the earliest design possible and can be used throughout the life-cycle of the building including retrofit analysis \citep{Miller:2014tu}. This process is achieved by augmenting the information in the BIM with default values and abstracting information not relevant for energy simulation. The tool already has a simplified notion of surrounding buildings, which are modeled in the BIM as simple mass objects without further information and are exported as shading surfaces to EnergyPlus. This functionality is used for creating the CitySim mass scene and leads to a crude model of the urban context of the building. The existing DPV philosophy of allowing the designer to iterate rapidly on early design decisions based on feedback about the performance of the design remains. This approach includes streamlining the process where running a simulation requires no effort from the designer due to automatic creation of input files, execution and analysis of the results.

@@

As of version 8.1.0, EnergyPlus supports exporting a simulation model as a Functional Mock-up Unit (FMU) \citep{Nouidui:2014hq}. This feature introduces new IDF objects to specify the interface such an FMU exposes. These objects define which output variables are exported by the FMU and which variables are imported. The FMU export functionality is closely linked to the Energy Management System (EMS) of EnergyPlus. Co-simulation exchange variables either mimic an EnergyPlus schedule, an EMS variable or drive an EMS actuator. It was determined that in order to export an output variable using the FMU export functionality, the variable itself must also be output with an IDF object of type \emph{Output:Variable} or \emph{EnergyManagementSystem:OutputVariable} in the IDF file as well. Since the model used by CitySim to simulate a building is more abstract than the model used by EnergyPlus, the EMS is used to aggregate certain values. CitySim does not model windows separately, therefore a weighted average of window and wall surface temperatures is calculated with EMS subroutines.

@@

The FMU creation process is the basis for coupling the two models at each timestep in the simulation. Figure \ref{fig:FMUOverview} illustrates this process from both the EnergyPlus and CitySim perspective. The augmented IDF file is fed to the \emph{EnergyPlusToFMI} script \citep{Nouidui:2014bo}. Once configured, this script produces an FMU file based on the augmented IDF file and the weather file to be used as well as a DLL file implementing the Functional Mock-up Interface that can load the IDF file, locate EnergyPlus and run the simulation. Table \ref{FMUimports} and \ref{FMUexports} outline the variables exchanged between EnergyPlus and CitySim through the FMI.

@@

On an hourly basis, CitySim performs a heating and cooling needs prediction step. The temperature determination step for the main building is replaced with the results of the EnergyPlus timestep as obtained through FMI library. The FMI library is used to send climatic and occupational data from CitySim to EnergyPlus (see Table \ref{FMUimports}), and to receive data from EnergyPlus that are further used within CitySim for the next time steps (see Table \ref{FMUimports}).

\begin{table}[H]
\tbl{Values imported by EnergyPlus from CitySim by the FMU}
{\begin{tabular}[l]{@{}lcc}\toprule
  \bf{Object (ep\_id)} &  \bf{Variable Name} & \bf{Description} \\
\colrule
  Outdoor & Outdoor Drybulb & The outdoor dry-bulb temperature in $^{\circ}\mathrm{C}$ \\
 & Outdoor Dewpoint & The outdoor dewpoint temperature in $^{\circ}\mathrm{C}$ \\
 & Outdoor Relative Humidity & The outdoor relative humidity expressed in percent. \\
 & Diffuse Solar & Diffuse horizontal irradiance in W/m$^2$ \\
 & Direct Solar & Beam normal irradiance in W/m$^2$ \\
 & Wind Speed & The outdoor wind speed in m/s \\
 & Wind Direction & The wind direction in degrees\\&&  (N=0, E=90, S=180, W=270) \\
 \hline
 Long Wave Radiation & Environmental Radiant Temp. & Calculated $T_{env}$ from the sky,\\&& ground, and surrounding surfaces \\
 & Environmental Radiant Heat & Calculated $h_{env}$ from the sky,\\&& ground, and surrounding surfaces \\
 & Gain Coefficient \\
 \hline
Zone & Occupation & Fraction of the maximum occupation\\&& (0.0-1.0) overrides the EnergyPlus occupation schedule\\&&  with the CitySim stochastic schedule. \\
\botrule
\end{tabular}}
\label{FMUimports}
\end{table}

\begin{table}[H]
\tbl{Values exported by EnergyPlus to CitySim by the FMU}
{\begin{tabular}[l]{@{}lcc}\toprule
  \bf{Object (ep\_id)} &  \bf{Variable Name} & \bf{Description} \\
\colrule
Wall, Roof & Outside Surface Temperature & The temperature on the outside of the surface in $^{\circ}\mathrm{C}$ \\    
    \hline
Wall & Average Outside Surface Temperature & The (weighted) average temperature of \\
& & the surface on the outside in $^{\circ}\mathrm{C}$. \\
    \hline
Zone & Total Heating Energy & The heating energy in Joules used in this timestep. \\
& Total Cooling Energy & The cooling energy in Joules used in this timestep. \\
& Zone Mean Air Temperature & The mean air temperature in the zone in $^{\circ}\mathrm{C}$ \\
& Ventilation Volume Flow Rate & The flow rate in $\mathrm{m}^3/\mathrm{s}$ (standard density) \\
\botrule
\end{tabular}}
\label{FMUexports}
\end{table}

@@

Long wave radiation exchange in the urban scale environment is also coupled in the co-simulation process. However, it requires the development of a set of approximations to reduce the number of coupled variables between the engines and to account for differences in the methods by which each engine calculates this metric. A detailed description of Long Wave Radiation (LWR) variable exchange and approximation is found in a previously published study \citep{Miller:2015vk} on a simplified theoretical case.

@@

\subsection{Work flow automation}
The coupling, simulation and co-simulation process is completely managed within a program called VisTrails. This tool empowers the coupling of various executable files and their connecting scripts in a graphical diagrams that enhances reproducibility and process automation \citep{Freire:2014tt}.

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.6]{figures/HPI_combinedclusterandcal_4}
\caption{HPI Electrical Energy Typical Profiles}
\label{fig:hpi_elec_profiles}
\end{figure}

The measured and simulated data from both the co-simulation and EnergyPlus solo simulation was compared in order to create a realistic scenario for comparison. The calibration process was undertaken through a series of steps such as including local weather conditions for the simulation period and adding custom lighting schedules and power densities extracted from the measured data. The models were calibrated to the summer season (May-September) for cooling and the winter season (Jan-April and October to December) for heating. This approach was taken as the data quality for the measurements were deemed most accurate during the appropriate seasons. Figure \ref{fig:hpi_measvssim} illustrates a comparison of the measured data with the simulations after the tuning process. The final calibrated EnergyPlus solo model had a normalized mean bias error (NMBE) of -9.36\% and a coefficient of variation of root mean square error (CVRMSE) of 21.7\% for cooling and -9.36\% and 29.4\% for heating. These metrics fall within the +/- 10\% and 30\% used in this case study for the purposes of partial calibration. The goal of calibration in this case is to simply bring the models to within a reasonable range of reality in order to bring more confidence to analysis of the discrepancies between the solo and co-simulation scenarios.
%Daily data was used to calculated goodness of fit to determine calibration success. 
%The final calibrated EnergyPlus solo model had a normalized mean bias error (NMBE) of -9.36\% and a coefficient of variation of root mean square error (CVRMSE) of 21.7\% for cooling and -9.36\% and 29.4\% for heating.

@@

After calibration, a comparison of co-simulation and solo EnergyPlus simulations is made. For cooling, a discrepancy can be seen between co-simulation and solo EnergyPlus. A 20.2\% decrease in predicted cooling energy is observed as seen in Figure \ref{hpi_energypluscooling}.

@@

\section{Conclusion}
The ability to couple and leverage the best aspects of multiple simulation engines can enhance the modeling of large scale urban agglomerations. This paper has outlined one such scenario in which the building-focused EnergyPlus simulation engine is coupled and co-simulated with the urban-scale CitySim engine. This process is implemented through a fully automated work flow process that extract geometry information at the urban-scale, creates the necessary input information, executes each engine with information exchange at each time step of targeted variables, and accumulates the results for analysis. The process has been implemented on simpflied theoretical scenarios in the past and the key innovation with this work is in implementation on actual case study campuses and targeted buildings. More reliable results of the magnitude of differences between the simulation techniques can be extracted from this scenario.

>>>>

\subsection{Coupling process}
The coupling process of a simplified single zone model and contextual surrounding buildings is outlined in previous studies \citep{thomas2014multiscale,Thomas:2012wj}. This study forms the basis for the methodology in the current effort. This process utilizes the Design Performance Viewer (DPV) and associated work flow. The DPV is a tool written to extract and simulate an EnergyPlus input data file (IDF) from an Autodesk\textsuperscript{TM} Revit\textsuperscript{TM} BIM \citep{Schlueter2009}. The main philosophy behind the tool is rapid simulation of the building information model from the earliest design possible and can be used throughout the life-cycle of the building including retrofit analysis \citep{Miller:2014tu}. This process is achieved by augmenting the information in the BIM with default values and abstracting information not relevant for energy simulation. The tool already has a simplified notion of surrounding buildings, which are modeled in the BIM as simple mass objects without further information and are exported as shading surfaces to EnergyPlus. This functionality is used for creating the CitySim mass scene and leads to a crude model of the urban context of the building. The existing DPV philosophy of allowing the designer to iterate rapidly on early design decisions based on feedback about the performance of the design remains. This approach includes streamlining the process where running a simulation requires no effort from the designer due to automatic creation of input files, execution and analysis of the results.

@@

As of version 8.1.0, EnergyPlus supports exporting a simulation model as a Functional Mock-up Unit (FMU) \citep{Nouidui:2014hq,Anonymous:ZZTfF80-}. This feature introduces new IDF objects to specify the interface such an FMU exposes. These objects define which output variables are exported by the FMU and which variables are imported. The FMU export functionality is closely linked to the Energy Management System (EMS) of EnergyPlus. Co-simulation exchange variables either mimic an EnergyPlus schedule, an EMS variable or drive an EMS actuator. Since the model used by CitySim to simulate a building is more abstract than the model used by EnergyPlus, the EMS is used to aggregate certain values. CitySim does not model windows separately, therefore a weighted average of window and wall surface temperatures is calculated with EMS subroutines.

% It was determined that in order to export an output variable using the FMU export functionality, the variable itself must also be output with an IDF object of type \emph{Output:Variable} or \emph{EnergyManagementSystem:OutputVariable} in the IDF file as well.

The FMU creation process is the basis for coupling the two models at each timestep in the simulation. Figure \ref{fig:FMUOverview} illustrates this process from both the EnergyPlus and CitySim perspective. The augmented IDF file is fed to the \emph{EnergyPlusToFMI} script \citep{Nouidui:2014bo}. Once configured, this script produces an FMU file based on the augmented IDF file and the weather file to be used as well as a DLL file implementing the Functional Mock-up Interface that can load the IDF file, locate EnergyPlus and run the simulation.

@@

% Table \ref{FMUimports} and \ref{FMUexports} outline the variables exchanged between EnergyPlus and CitySim through the FMI.

@@

% On an hourly basis, CitySim performs a heating and cooling needs prediction step. The temperature determination step for the main building is replaced with the results of the EnergyPlus timestep as obtained through FMI library. The FMI library is used to send climatic and occupational data from CitySim to EnergyPlus, and to receive data from EnergyPlus that are further used within CitySim for the next time steps. 
Several key urban-scale weather variables are sent to EnergyPlus from CitySim in order to better account for the localized effects of surrounding buildings, geography and climactic conditions. These variables include various outdoor air conditions such as drybulb and wetbulb temperatures, dewpoint, humidity, wind speed and direction, and direct and diffuse solar radiation. These variables overwrite the input weather variables that EnergyPlus obtains from its weather file input. One of the key objectives of CitySim as a a simulation engine has been its to account for physical phenomenon inherent to urban environments that is often neglected in building-scale simulation environments \citep{Robinson:2004cr,Robinson:2009tm}. Long wave radiation exchange between the simulated building and its surroundings is sent to EnergyPlus; this process is describe in detail in a subsequent methodology section. Finally, CitySim shares its calculated occupancy schedules as it uses a more robust model of occupants behavior \citep{Haldi:2011dr}.

\begin{table}[H]
\tbl{Values sent to EnergyPlus from CitySim by the FMU}
{\begin{tabular}[l]{@{}lcc}\toprule
  \bf{Object} &  \bf{Variable Name} & \bf{Description} \\
\colrule
  Outdoor & Outdoor Drybulb & The outdoor dry-bulb temperature in $^{\circ}\mathrm{C}$ \\
 & Outdoor Dewpoint & The outdoor dewpoint temperature in $^{\circ}\mathrm{C}$ \\
 & Outdoor Relative Humidity & The outdoor relative humidity expressed in percent. \\
 & Diffuse Solar & Diffuse horizontal irradiance in W/m$^2$ \\
 & Direct Solar & Beam normal irradiance in W/m$^2$ \\
 & Wind Speed & The outdoor wind speed in m/s \\
 & Wind Direction & The wind direction in degrees\\&&  (N=0, E=90, S=180, W=270) \\
 \hline
 Long Wave Radiation & Environmental Radiant Temp. & Calculated $T_{env}$ from the sky,\\&& ground, and surrounding surfaces \\
 & Environmental Radiant Heat & Calculated $h_{env}$ from the sky,\\&& ground, and surrounding surfaces \\
 & Gain Coefficient \\
 \hline
Zone & Occupation & Fraction of the maximum occupation\\&& (0.0-1.0) overrides the EnergyPlus occupation schedule\\&&  with the CitySim stochastic schedule. \\
\botrule
\end{tabular}}
\label{FMUimports}
\end{table}

Variables sent to CitySim by EnergyPlus at each timestep include several variables related to the calculation of heating and cooling loads of a targeted building. These variables are transferred due to the ability of EnergyPlus to model more detailed building systems, schedules, ventilation and internal load types than CitySim. For example, EnergyPlus is flexible enough to model a detailed, radiant heating and cooling system that would be impossible in CiytSim \cite{barbara:2015tz}. EnergyPlus is an engine optimized on the accuracy of building-scale systems, thus CitySim can take advantage of these models through coupling and co-simulation. EnergyPlus sends the heating and cooling loads, the surface temperatures of the exterior surfaces and the ventilation flow rates to CitySim.

\begin{table}[H]
\tbl{Values to CitySim from EnergyPlus by the FMU}
{\begin{tabular}[l]{@{}lcc}\toprule
  \bf{Object} &  \bf{Variable Name} & \bf{Description} \\
\colrule
Wall, Roof & Outside Surface Temperature & The temperature on the outside of the surface in $^{\circ}\mathrm{C}$ \\    
    \hline
Wall & Average Outside Surface Temperature & The (weighted) average temperature of \\
& & the surface on the outside in $^{\circ}\mathrm{C}$. \\
    \hline
Zone & Total Heating Energy & The heating energy in Joules used in this timestep. \\
& Total Cooling Energy & The cooling energy in Joules used in this timestep. \\
& Zone Mean Air Temperature & The mean air temperature in the zone in $^{\circ}\mathrm{C}$ \\
& Ventilation Volume Flow Rate & The flow rate in $\mathrm{m}^3/\mathrm{s}$ (standard density) \\
\botrule
\end{tabular}}
\label{FMUexports}
\end{table}

@@

Long wave radiation exchange in the urban scale environment is coupled in the co-simulation process and it requires the development of a set of approximations to reduce the number of coupled variables between the engines and to account for differences in the methods by which each engine calculates this metric. A detailed description of Long Wave Radiation (LWR) variable exchange and approximation is found in a previously published study \citep{Miller:2015vk} on a simplified theoretical case.

@@

\subsection{Work flow automation}
The coupling, simulation and co-simulation process is completely managed within a program called VisTrails \citep{Anonymous:Cayf2tu7}. This tool empowers the coupling of various executable files and their connecting scripts in a graphical diagrams that enhances reproducibility and process automation \citep{Freire:2014tt}.

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.55]{figures/HPI_combinedclusterandcal_5}
\caption{HPI Electrical Energy Typical Profiles}
\label{fig:hpi_elec_profiles}
\end{figure}

The measured and simulated data from both the co-simulation and EnergyPlus solo simulation was compared in order to create a realistic scenario for comparison. The calibration process was undertaken through a series of steps such as including local weather conditions for the simulation period and adding custom lighting schedules and power densities extracted from the measured data. The models were calibrated to the summer season (May-September) for cooling and the winter season (Jan-April and October to December) for heating. This approach was taken as the data quality for the measurements were deemed most accurate during the appropriate seasons. Figure \ref{fig:hpi_measvssim} illustrates a comparison of the measured data with the simulations after the tuning process. The final calibrated EnergyPlus solo model had a normalized mean bias error (NMBE) of -9.36\% and a coefficient of variation of root mean square error (CVRMSE) of 21.7\% for cooling and -9.36\% and 29.4\% for heating. These metrics fall within the +/-10\% NMBE and +/-30\% CVRSME used in this case study for the purposes of partial calibration. The goal of calibration in this case is to simply bring the models to within a reasonable range of reality in order to bring more confidence to analysis of the discrepancies between the solo and co-simulation scenarios.
%Daily data was used to calculated goodness of fit to determine calibration success. 
%The final calibrated EnergyPlus solo model had a normalized mean bias error (NMBE) of -9.36\% and a coefficient of variation of root mean square error (CVRMSE) of 21.7\% for cooling and -9.36\% and 29.4\% for heating.

@@

After calibration, a comparison of co-simulation and solo EnergyPlus simulations is made. For cooling, a discrepancy can be seen between co-simulation and solo EnergyPlus. A 20.2\% decrease in predicted cooling energy is observed as seen in Figure \ref{fig:hpi_energypluscooling}.

@@

\section{Conclusion}
The ability to couple and leverage the best aspects of multiple simulation engines can enhance the modeling of large scale urban agglomerations. This paper has outlined one such scenario in which the building-focused EnergyPlus simulation engine is coupled and co-simulated with the urban-scale CitySim engine. This process is implemented through a fully automated work flow process that extract geometry information at the urban-scale, creates the necessary input information, executes each engine with information exchange at each timestep of targeted variables, and accumulates the results for analysis. The process has been implemented on simpflied theoretical scenarios in the past and the key innovation with this work is in implementation on actual case study campuses and targeted buildings. More reliable results of the magnitude of differences between the simulation techniques can be extracted from this scenario.
